System Architecture for a Class of Small Service Vehicle

### 2015-10-21 ieee-pandoc-template/paper.tex
conformed with the conference format; WARNING: use the .cls from latest distro

\documentclass[conference]{IEEEtran}
%\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
%\documentclass[conference]{IEEEconf}

@@

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\author{
            \IEEEauthorblockN{Saputra, V. B.}
        \IEEEauthorblockA{%
            Institute for Infocomm Research \\
            Singapore \\
            saputravb@i2r.a-star.edu.sg}
         \and
            \IEEEauthorblockN{Ravichandiran, B.}
        \IEEEauthorblockA{%
            Institute for Infocomm Research \\
            Singapore \\
            ravib@i2r.a-star.edu.sg}
        }

@@

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{IEEEkeywords}
    automobiles;
    feature extraction;
    intelligent transportation systems;
    mobile robots;
    optical scanners;
    path planning;
    trajectory control;
    autonomous service vehicle;
    drive-by-wire system;
    driverless car;
    electronic car;
    lane detection algorithm;
    lane keeping assistant;
    laser scanner;
    map free lane following;
    path planning;
    vehicle trajectory;
    Laser radar;
    Mobile robots;
    Path planning;
    Roads;
    Testing;
    Vehicles;
    Wheels\end{IEEEkeywords}

@@

\paragraph{Road curb}\label{road-curb}
Road curb is the most reliable feature in road boundary detection. It is
easy to detect and currently it is the baseline for localization.

>>>>

%\documentclass[10 pt,letterpaper,conference]{IEEEtran}
%\documentclass[10 pt,letterpaper,conference]{IEEEconf}
\documentclass[10 pt,letterpaper,conference]{IEEEtran}

@@

%\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

@@

\author{
		\IEEEauthorblockN{Saputra, V. B.}
	\IEEEauthorblockA{%
		Institute for Infocomm Research \\
		1 Fusionopolis Way, Singapore 138632 \\
	saputravb@i2r.a-star.edu.sg}
	 \and
		\IEEEauthorblockN{Ravichandiran, B.}
	\IEEEauthorblockA{%
		Institute for Infocomm Research \\
		1 Fusionopolis Way, Singapore 138632 \\
	ravib@i2r.a-star.edu.sg}
	}

@@

% Redefines (sub)paragraphs to behave more like sections
%\ifx\paragraph\undefined\else
%\let\oldparagraph\paragraph
%\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
%\fi
%\ifx\subparagraph\undefined\else
%\let\oldsubparagraph\subparagraph
%\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
%\fi

@@

%%\begin{IEEEkeywords}
%    %automobiles;
%    %feature extraction;
%    %intelligent transportation systems;
%    %mobile robots;
%    %optical scanners;
%    %path planning;
%    %trajectory control;
%    %autonomous service vehicle;
%    %drive-by-wire system;
%    %driverless car;
%    %electronic car;
%    %lane detection algorithm;
%    %lane keeping assistant;
%    %laser scanner;
%    %map free lane following;
%    %path planning;
%    %vehicle trajectory;
%    %Laser radar;
%    %Mobile robots;
%    %Path planning;
%    %Roads;
%    %Testing;
%    %Vehicles;
%    %Wheels%\end{IEEEkeywords}
%

@@

\paragraph{Road curb}\label{road-curb}

Road curb is the most reliable feature in road boundary detection. It is
easy to detect and currently it is the baseline for localization.
